The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-07 Writeup/paper_v3.tex
a bit more conclusion to 4.2

Finally, Fig.~\ref{fig:median_dvcbtt} shows the variation of the median
bulge-to-total ratio with redshift. The results are quite consistent
with those of Fig.~\ref{fig:median_sersicn}.

>>>>

Finally, Fig.~\ref{fig:median_dvcbtt} shows the variation of the median
bulge-to-total ratio with redshift. The results are quite consistent
with those of Fig.~\ref{fig:median_sersicn}. 
Thus, our results in this section suggest that the 
environment can significantly affect the median morphological
parameters of galaxies selected in thin redshift
slices, assuming that the galaxies represent a stellar mass-selected
sample.  The trend is less evident when using luminosity to select the
galaxies.
